---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%",
  root.dir = "C:/Users/tdeswaef/AquaCrop_70/"
)
knitr::opts_knit$set(root.dir = "C:/Users/tdeswaef/AquaCrop_70/")
#setwd("C:/Users/tdeswaef/AquaCrop_70/")
# getwd()
```

# AquacropOnR

<!-- badges: start -->

<!-- badges: end -->

The goal of AquacropOnR is to make AquaCrop simulations from within `R` as easy as possible. The package has currently been tested with the AquaCrop standalone version 7.0 on Windows. The most recent version can be downloaded from the [FAO website](https://www.fao.org/aquacrop/software/aquacropplug-inprogramme/en/#c518670).

## Installation and setup

First install [git](https://git-scm.com/downloads).
Then you can install the development version of `AquacropOnR` using the `devtools` package:

``` r
library(devtools)
devtools::install_git(url = "https://github.com/tdeswaef/aquacroponr.git", force = TRUE)
```

The installation of the AquaCrop standalone version is required.

## Example

This is a basic example to run AquaCrop from `R` for the spinach crop.

Importantly, the working directory should be set to the folder in which the *aquacrop.exe* file is located.

```{r aquafolder, include=FALSE}
path_to_aquacrop_folder <- "C:/Users/tdeswaef/AquaCrop_70/"

```

```{r lib, warning=FALSE, message=FALSE, prompt=FALSE} 

 library(AquacropOnR)
 library(tidyverse)
 library(reshape2)
setwd(dir = path_to_aquacrop_folder)
```

With the package comes an example list with default crop parameters for **quinoa** and **spinach**. To make this list for your own crop, you need an AquaCrop cropfile (*YourCrop.CRO*) whose path should be input in the `read_CRO()` function:

``` r
yourcrop <- read_CRO("path/YourCrop.CRO")` 
```

Once you have the list with default crop parameter values, you can design the scenario's for which you want to run AquaCrop. The `AquacropOnR` package provides a function to design the scenario's: `design_scenario()`. The arguments in this function have the following meaning:

-   `name` is a character vector of names for the scenario's.
-   `Input_Date` is a Date vector that indicates the start point of the meteo files (`Plu`, `Tnx`, `ETo`)  
-   `Plant_Date` is a Date vector that defines the planting date in each scenario  
-   `IRRI` is a character vector of the names of the irrigation scenario's present in the `ID` column of the `IRRI_s` tibble.  
-   `Soil` is a character vector of the names of the soils present in the `ID` column of the `SOL_s` tibble. 
- `Plu`, `Tnx`, and `ETo` are character (vectors) that refer to the names of `R` objects, that hold the daily data for precipitation, temperature and reference evapotranspiration, respectively. 

**IMPORTANT**: 

- The Scenario_s tibble **must** be named `Scenario_s` and **must** have the columns (variables) `Scenario`, `Input_Date`, `Plant_Date`, `IRRI`, `Soil` and `Meteo`.  
- The irrigation tibble **must** be named `IRRI_s` and **must** have the columns `ID`, `Timing`, `Depth` and `ECw`. Values of the `ID` column are given as input to the `IRRI` argument in the `design_scenario()` function.  
- The soil tibble **must** be named `SOL_s` and **must** have the columns `ID`, `Horizon`, `Thickness`, `SAT`, `FC`, `WP`, `Ksat`, `Penetrability` and `Gravel`. Values of the `ID` column are given as input to the `Soil` argument in the `design_scenario()` function.  
- The precipitation tibble can be named as you want, but its name is the input to the `Plu` argument in the `design_scenario()` function. This tibble **must** have the columns `DAY` and `PLU`.  
- The reference evapotranspiration tibble can be named as you want, but its name is the input to the `ETo` argument in the `design_scenario()` function. This tibble **must** have the columns `DAY` and `ETo`.  
- The temperature tibble can be named as you want, but its name is the input to the `Tnx` argument in the `design_scenario()` function. This tibble **must** have the columns `DAY`, `TMAX` and `TMIN`.


Examples of these tibbles are available from the package.

```{r example 1}
Scenario_s <- design_scenario(name = "S_01",
                              Input_Date = as.Date("2019-01-01"),
                              Plant_Date = as.Date("2019-04-01"), 
                              IRRI = "IRRI_01", 
                              Soil = "Soil_01", 
                              Plu = "Plu_01",
                              Tnx = "Tnx_01",
                              ETo = "ETo_01")
Scenario_s
IRRI_s <- tibble(ID = "IRRI_01", Timing = 20, Depth = 25, ECw = 30)
SOL_s
Plu_01
Tnx_01
ETo_01
```

Then it is crucial to create the correct AquaCrop path, while checking the required folders and choosing which daily outputs to produce. Therefore the package has the function `path_config()`. Make sure your path ends with a "/".

```{r example2} 
AQ <- path_config(AquaCrop.path = path_to_aquacrop_folder, Daily_output = c(1,2))
```

Finally, we can run AquaCrop using the `aquacrop_wrapper()` function and display a plot. The `param_values` argument is used to modify crop parameters from the default, which is the list provided as input to the `defaultpar` argument inside the `model_options` list. `situation` takes a vector of characters, that correspond to the `Scenario` variable in the `Scenario_s` tibble.

Let us first run the simulation with the default parameters for spinach:

```{r example3, warning=FALSE, message=FALSE} 
default <- aquacrop_wrapper(param_values = list(),
               situation = "S_01",
               cycle_length = 70,
               model_options = list(AQ = AQ, defaultpar = Spinach, output = "morris"))
ggplot(mapping = aes(x=DAP, y=Biomass)) +
  ylim(0, 3.5) +
  geom_line(data = default, color = 'black', linewidth = 1) +
  geom_text(mapping = aes(x=40, y=3, label = 'default'), color = 'black') +
  xlim(0, 70) +
  theme_bw()
```



And now let's see what happens when we increase the canopy growth coefficient `cgc` from 0.15 to 0.18:

```{r example4,warning=FALSE, message=FALSE}
modified <- aquacrop_wrapper(param_values = list(cgc = 0.18),
               situation = "S_01",
               cycle_length = 70,
               model_options = list(AQ = AQ, defaultpar = Spinach, output = "def"))

ggplot(mapping = aes(x=DAP, y=Biomass)) +
  ylim(0, 3.5) +
  geom_line(data = default, color = 'black', linewidth = 1) +
  geom_text(mapping = aes(x=40, y=3, label = 'default'), color = 'black') +
  geom_line(data = modified, color = 'blue', linewidth = 1) +
  geom_text(mapping = aes(x=40, y=2.8, label = 'modified'), color = 'blue') +
  xlim(0, 70) +
  theme_bw()

```

A list of parameters with their explanation can be found in the [crop parameter file](Cropparameters.md)

## Example Morris method

For sensitivity analysis using the `morris` method you first design the morris sampling scheme and the simulations.
Based on these results, you can then define for which level you want to calculate the elemental effects.
First we run the Morris method using the `aquacrop_morris` function: 


```{r morris1, warning=FALSE, message=FALSE}

p <- aquacrop_morris(situation = "S_01", 
                     backgroundpar=Spinach, 
                     cycle_length = 70, 
                     r = 20, 
                     binf=c(rt_max = 0.12, cgc = 0.1), 
                     bsup = c(rt_max = 0.55, cgc = 0.21), 
                     outvars = c("Biomass", "YSdryS"))

``` 

Then we create the interpretable dataframe from the elemental effects matrix: 

```{r morris2, warning=FALSE,message=FALSE}
EE <- p$ee %>% melt(value.name = "ee", varnames = c("traject", "par", "DAP", "output"))

```

If you would have multiple scenarios in your analysis, then the DAP values can be split up by scenario:

```{r morris3, warning=FALSE, message=FALSE}

EE <- EE %>% dplyr::mutate(Scenario = (DAP %/% 70)+1,
                           DAP = DAP %% 70)

```

We can then choose the level of integration at which we want to summarise the elemental effects:

- By DAP and output variable

```{r morris4, warning=FALSE, message=FALSE}
mu_star1 <- EE %>%
  group_by(par, DAP, output) %>%
  summarise(mu = mean(ee),
            mu_star = mean(abs(ee)),
            sigma = sd(ee))

ggplot(mu_star1) +
  facet_wrap(facets = vars(output), nrow=2) +
  theme_bw() +
  geom_point(mapping = aes(x=DAP, y=mu_star, color = par))

```

- By output variable

```{r morris5, warning=FALSE, message=FALSE}
mu_star2 <- EE %>% 
  group_by(par, output) %>%
  summarise(mu = mean(ee),
            mu_star = mean(abs(ee)),
            sigma = sd(ee))

ggplot(mu_star2) +
  facet_wrap(facets = vars(output), nrow=2) +
  theme_bw() +
  geom_point(mapping = aes(x=mu_star, y=sigma, color = par))

```


## Roadmap

- [x] definition of the AquaCrop wrapper function `aquacrop_wrapper`  
- [x] allow option to run AquaCrop on growing degree days instead of days  
- [x] include code for running sensitivity analysis using the morris method  


