---
title: "Example for scenario making"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example-scenario}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
datapath <- "../aquacrop71/"
```

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(AquacropOnR)
```

## Meteo data
Here we provide an example for a weather data set: 

- `TEMP_MAX` is the maximum daily temperature in  \deg C    
- `TEMP_MIN` is the minimum daily temperature in \deg C  
- `RELATIVE_HUMIDITY` is the average relative humidity in \%  
- `WIND_SPEED` is the average daily wind speed in m/s  
- `PRECIP_QUANTITY` is the total daily precipitation in mm  
- `GLOBAL_RADIATION` is expressed in kWh/m².  

```{r meteo_1}
Meteo_data <- read_delim(paste0(datapath, "data.csv"), delim = ",", show_col_types = F)
head(Meteo_data)
```
This data set has some missing data. We solve this here by using the `approxfun` function to iterpolate missing values.

```{r meteo_2}

Meteo_data <- Meteo_data %>%
  mutate(DATE = as_date(paste(YEAR, MONTH, DAY, sep = "-")))

START <- "2020-01-01"
STOP <- "2020-12-31"

Tmax_fun <- approxfun(Meteo_data$DATE, Meteo_data$TEMP_MAX)
Tmin_fun <- approxfun(Meteo_data$DATE, Meteo_data$TEMP_MIN)
RH_fun <- approxfun(Meteo_data$DATE, Meteo_data$RELATIVE_HUMIDITY)
Wind_fun <- approxfun(Meteo_data$DATE, Meteo_data$WIND_SPEED)
Precip_fun <- approxfun(Meteo_data$DATE, Meteo_data$PRECIP_QUANTITY)
Radiation_fun <- approxfun(Meteo_data$DATE, Meteo_data$GLOBAL_RADIATION)

Alldays <- seq.Date(from = as_date(START), to = as_date(STOP), by = 1)

Meteo_data <- tibble(YEAR = lubridate::year(Alldays),
                     MONTH = lubridate::month(Alldays),
                     DAY = lubridate::day(Alldays),
                     TEMP_MAX = Tmax_fun(Alldays),
                     TEMP_MIN = Tmin_fun(Alldays),
                     RELATIVE_HUMIDITY = RH_fun(Alldays),
                     WIND_SPEED = Wind_fun(Alldays),
                     PRECIPITATION = Precip_fun(Alldays),
                     GLOBAL_RADIATION = Radiation_fun(Alldays),
                     DATE = Alldays)



```

As AquaCrop requires reference evapotranspiration as an input, we calculate this using the `ETo_calc()` function available through the `MeteoTools` package, based on the `Evapotranspiration` package.

```{r meteo_3, warning=FALSE, message = FALSE}
library(MeteoTools)

ETo_data <- ETo_calc(DATE = Meteo_data$DATE, 
                     T_max = Meteo_data$TEMP_MAX, 
                     T_min = Meteo_data$TEMP_MIN, 
                     RH_max = pmin(Meteo_data$RELATIVE_HUMIDITY, 100), 
                     RH_min = pmin(Meteo_data$RELATIVE_HUMIDITY, 100),
                     Rs_tot = Meteo_data$GLOBAL_RADIATION*3.6, # from kWh m^-2 to MJ m^-2
                     uz_mean = Meteo_data$WIND_SPEED)

head(ETo_data)

```
Now we put everything in the AquacropOnR format: 

```{r meteo_4}
Plu_example <- Meteo_data %>% 
  dplyr::mutate(DAY = lubridate::yday(DATE), PLU = PRECIPITATION) %>% 
  dplyr::select(DAY, PLU)
Tnx_example <- Meteo_data %>% 
  dplyr::mutate(DAY = lubridate::yday(DATE), TMAX = TEMP_MAX, TMIN = TEMP_MIN) %>% 
  dplyr::select(DAY, TMAX, TMIN) 

ETo_example <- ETo_data %>% 
  dplyr::mutate(DAY = lubridate::yday(DATE)) %>% 
  dplyr::select(DAY, ETo)

```
## Soil data

```{r soil_1}

SOL_s <- tribble(~ID, ~Horizon, ~Thickness, ~SAT, ~FC, ~WP, ~Ksat, ~Penetrability, ~Gravel,
                "soil_1", 1, 0.1, 40.8, 29.2, 12.5, 120,  100, 0,
                "soil_1", 2, 0.2, 44.3, 32.2, 10.5, 96,   100, 0,
                "soil_1", 3, 0.6, 32.2, 21.4, 11.5, 52.5, 100, 0,
                "soil_1", 4, 1.1, 30.1, 20.2, 10.5, 55,   100, 0,
                "soil_2", 1, 0.1, 35.8, 29.2, 12.5, 1200, 100, 0,
                "soil_2", 2, 0.5, 31.8, 24.5, 10.5, 1200, 100, 0,
                "soil_2", 3, 2.2, 31.2, 22.2, 9.5,  950,  100, 0)
head(SOL_s)
```

## Initial conditions
If you do not provide initial conditions in the `design_scenario()` function, it will take the default setting "FC", which results in a soil profile water content at field capacity and absence of salts at the start of the simulation. 

The initial conditions need to have the same Horizon and Thickness variables as the soil input tibble `SOL_s`. here we provide an example where the initial water content at all layers lies in the middle between wilting point (WP) and field capacity (FC).
 
```{r initials}
sw0_factor <- 0.5
SW0_s <- SOL_s %>% mutate(WC = WP + (FC-WP)*sw0_factor, ECe = 0.0) %>%
  select(ID, Horizon, Thickness, WC, ECe)
head(SW0_s)
```

## Management
Through the .MAN file, AquaCrop can take into account several field management settings, such as: 

- the effect of mulching, using the percentage of soil covered by mulch (`mulch_perc`), and the effect on reducing soil evaporation (`mulch_eff` between 0 (no effect) and 100 (all evaporation inhibited)).  
- the fertility stress (`fert_stress`, between 0 (no stress) and 100 (complete stress)).  
- the presence of soil bunds (`soil_bunds`).  
- the use of run-off affecting measures (`runoff_aff`, 0 or 1 (for complete prevention of run-off)) and their effect on the *curve number* (`CN_eff`).  
- presence of weeds (`weed_clo`, `weed_mid`, `weed_cc`).

For an effect of erosion preventing measures, the management file can be defined as follows:

```{r manag}

FMAN_s <- tribble(~ID, ~mulch_perc, ~mulch_eff, ~fert_stress, ~soil_bunds, ~runoff_aff, ~CN_eff, ~weed_clo, ~weed_mid, ~weed_cc,
                  "default", 0, 50, 0, 0, 0, 0, 0, 0, -0.01,
                  "reduction_1", 0, 50, 0, 0, 0, -25, 0, 0, -0.01)

```

where the *default* treatment has no measures and the *reduction_1* treatment ahas measures that reduce the curve number by 25.
